Elephant Seal Age JAE Intraspecific Variation

### 2024-04-25 paper/paperv3.qmd
Making a figure to illustrate detection probability

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987) %>% 
  mutate(across(c(animalID, year), factor),
         age10 = age / 10)
```

@@

n = `r n_distinct(sealdat$animalID)` distinct animals

>>>>

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987) %>% 
  mutate(across(c(animalID, year), factor),
         age10 = age / 10)

resight <- read.csv(here::here("data/raw/fullresights.csv"))

@@

First, address detection probability. We do resights near-daily during breeding and molting seasons, so while we may miss an individual on a given day, it is unlikely that we miss a marked individual throughout the entire breeding or molting season.

```{r}
#| label: detection-prob

resight <- resight %>% 
  dplyr::select(animalID, resightID, season, date, timeofyear, calyear) %>% 
  mutate(animalID = as.factor(animalID))

full <- semi_join(resight, sealdat, "animalID") %>% group_by(animalID, calyear) %>% count(calyear)

ggplot(full, aes(calyear, n)) + 
  geom_point()

#

n = `r n_distinct(sealdat$animalID)` distinct animals.
